\documentclass[15pt]{scrartcl}
\usepackage[sexy]{evan}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\usepackage{relsize}
\begin{document}
\title{Math Daily Log}
\date{\today}
\author{Jiawen Huang}
\maketitle
\section*{Acknowlegdement}
This is Evan Style LaTeX template. Thanks to Evan Chen for creating such a beautiful style file.
\section*{October 28, 2025}
\begin{enumerate}
\item Weyl Algebra $\frac{k<x,y>}{xy-yx-1}$. 
\item Center of Weyl Algebra is $k$ in characteristic 0.
\item In characteristic $p$, the center of Weyl Algebra is $k[x^p,y^p]$.
\item Weyl Algebra is simple.
\item $x$ and $y$ can be seen as operators on $k[t]$ by $x:f\mapsto tf$ and $y:f\mapsto \frac{df}{dt}$. This is amazing. 
I think the structure $xy-yx=1$ can be used to make some algebra olympiads problems. Very rich and interesting structure. 
When you interpret as operators on polynomials, everything becomes very concrete and easy to understand. Perfect for a math olympiad problem.

\end{enumerate}

\section*{October 29, 2025}
\begin{enumerate}
\item spiltting field is unique up to isomorphism.
\item Separable. An insparable polynomial: $x^p-t$ over $\mathbb{F}_p(t)$. $x^p-t=(x-u)^p$ in the algebraic closure. 
\item A polynomial is separable iff its derivative and $f$ are coprime. In particuplar, over characteristic 0, all irreducible polynomials are separable.
\item A field is perfect if all irreducible polynomials are separable iff every algebraic extension is separable. 
\item A finite extension is separable iff $[F:k]_s=[F:k]$ iff $F=k(\alpha_1,...,\alpha_n)$ where $\alpha_i$ are separable.
\item A finite Normal extensions is a spiltting field of a polynomial. This is amazing. 
\item Riemann integral is equivalent to Darboux integral.
\end{enumerate}
\section*{October 30, 2025}
\begin{enumerate}
\item Riemann integrable iff discontinuities has measure 0.
\item A lot of exercises on separable extensions from Aluffi chapter 7. 
\item Formal power series $k[[x]]$ on math 250 lecture. 
\end{enumerate}



\end{document}